Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-07-11 WholePlotTrajectories.Rmd
ref

## abstract: 204 words / text without legends : 3659 words

@@

The long-term impact of disturbance on community functional redundancy meant a lower resilience of the pre-disturbance communities, with higher chances to see the persistence of disturbance-specific species at the expense of late-successional ones [@Haddad2008].
Besides the long-term recovery of infrequent species increases the risks to loose cornerstone species, with unexpected ecological consequences [@Jones1994;@Chazdon2003a;@Diaz2005;@Gardner2007].
Apart from the functional characteristics considered here, infrequent species might indeed have unique functions in the ecosystem or be a key for some fauna.

>>>>

## abstract: 204 words / text without legends : 3659 words / references: 68

@@

The long-term impact of disturbance on community functional redundancy meant a lower resilience of the pre-disturbance communities, with higher chances to see the persistence of disturbance-specific species at the expense of late-successional ones [@Haddad2008].
Besides the long-term recovery of infrequent species increases the risks to loose cornerstone species, with unexpected ecological consequences [@Jones1994;@Chazdon2003a;@Diaz2005].
Apart from the functional characteristics considered here, infrequent species might indeed have unique functions in the ecosystem or be a key for some fauna.
